### 2014-10-20 Publications/2013-TMI/02-abstract.tex
update

We propose a surface-to-volume variational solution to the registration problem,
  that exploits the detailed anatomy extracted manually or from structural images.
We use an ``active contours without edges''-like model to search for a
  deformation field that optimally maps the surface prior onto the data
  in the target space, implicitly segmenting with sub-pixel resolution the
  volume.
We demonstrate the usefulness of the approach on a digital phantom, and on
  10 real datasets randomly selected from the Human Connectome Project.

>>>>

We propose a surface-to-volume variational solution to the registration problem,
  that exploits the detailed anatomy extracted manually or automatically
  from structural images.
We use an ``active contours without edges'' model to search for a
  deformation field of B-Spline functions that optimally maps the
  surface prior onto the data in the target space.
The strategy implicitly segments with sub-pixel resolution the image.
We demonstrate the usefulness of the approach on a digital phantom, and on
  10 real datasets randomly selected from the Human Connectome Project.

### 2014-10-20 Publications/2013-TMI/03-introduction.tex
update

In this paper we propose a novel registration framework to simultaneously
solving the segmentation, distortion and cortical parcellation challenges,
by exploiting as strong shape-prior the detailed morphology extracted
from high-resolution and anatomically correct \gls{mri}.
Indeed, hereafter
we assume this segmentation problem in anatomical images is reliably and
accurately solved with readily available tools (e.g.
\citep{fischl_freesurfer_2012}).
After global alignment with \gls{t1} using existing approaches, the remaining
spatial mismatch between anatomical and diffusion space is due to susceptibility
distortions.
Finally, we need to establish precise spatial correspondence between the
surfaces in both spaces, including the tangential direction for parcellation.
Therefore, we can reduce the problem to finding the differences of spatial
distortion in between anatomical and \gls{dwi} space.
We thus reformulate the segmentation problem as an inverse problem, where we
seek for an underlying deformation field (the distortion) mapping
from the structural space into the diffusion space, such that the structural
contours segment optimally the \gls{dwi} data.
In the process, the one-to-one
correspondence between the contours in both spaces is guaranteed, and projection
of parcellisation to \gls{dwi} space is implicit and consistent.

>>>>

-> Volume-based registration is a traditional technique

-> We have anatomical surfaces at high resolution that we want to impose to a
lower resolution (typically different sequence), a follow-up image to track the surface
or similar.

-> Similar problem: atlas-based registration.

Atlas-based segmentation Nonlinear registration and  are fundamental techniques applied in
  image processing.
In this paper we propose a novel registration framework to simultaneously
solving the segmentation, distortion and cortical parcellation challenges,
by exploiting as strong shape-prior the detailed morphology extracted
from high-resolution and anatomically correct \gls{mri}.
Indeed, hereafter
we assume this segmentation problem in anatomical images is reliably and
accurately solved with readily available tools (e.g.
\citep{fischl_freesurfer_2012}).
After global alignment with \gls{t1} using existing approaches, the remaining
spatial mismatch between anatomical and diffusion space is due to susceptibility
distortions.
Finally, we need to establish precise spatial correspondence between the
surfaces in both spaces, including the tangential direction for parcellation.
Therefore, we can reduce the problem to finding the differences of spatial
distortion in between anatomical and \gls{dwi} space.
We thus reformulate the segmentation problem as an inverse problem, where we
seek for an underlying deformation field (the distortion) mapping
from the structural space into the diffusion space, such that the structural
contours segment optimally the \gls{dwi} data.
In the process, the one-to-one
correspondence between the contours in both spaces is guaranteed, and projection
of parcellisation to \gls{dwi} space is implicit and consistent.
